### 2016-08-17 rebuttal.tex

\begin{solution}
We have added a citation for mpmath.
\end{solution}
\end{questions}

\section{Reviewer 3 (Vedran Sego)}

\begin{questions}

\question Explaining what Python is (lines 70--72) should go before talking about SymPy as a ``CAS written in Python''. Further, the paper assumes a moderate familiarity with Python (for example, Python's console, OOP, and exceptions), and this should be specified. There should be a short note on the used Python console (\texttt{>>>} is the prompt, with the results of computation following immediately in the lines after it). The citation [25] from line 65 should be moved next to ``Python'' in line 70.
\begin{solution}
Citation was moved and footnote for Python interactive prompt was
added where it was used first time.
We believe that the paper assumes minimal familiarity with Python and
that should be covered either with citation [25] or with the Python tutorial.
\end{solution}

@@

Emphasize that the environment variable \texttt{SYMPY\_DEBUG} must be set before importing SymPy for the first time.
\begin{solution}

\end{solution}

\question In line 183, syntax \texttt{symbols(\textquotesingle{}a:d\textquotesingle{})} is used without being previously defined or explained.
\begin{solution}
Now we use \texttt{symbols('a b c d')}, like in other places.
\end{solution}

\question Figure 2 should not be a screenshot, but rather proper code with \LaTeX-rendered results and explanations, as was done in the rest of the paper. A
 shortened link to SymPy Gamma for the example's expression can be included
 for the user to try this for themselves.
\begin{solution}
We believe this is not a good idea.  SymPy Gamma currently
don't export output as Jupyter notebook or other external
format, but HTML.

URL to the project site was added.
\end{solution}

### 2016-08-17 gruntz.tex
Address question 44 from the reviewer 3

In this example the result ($2+{1\over x}$) still depends on $x$, so the above procedure is
repeated until just a value independent of $x$ is obtained. This is the final
limit. In the above case the limit is $2$, as can be
verified by SymPy:

>>>>

In this example the result ($2+{1\over x}$) still depends on $x$, so the above procedure is
repeated until just a value independent of $x$ is obtained. This is the final
limit. In the above case the limit is $2$, as can be
verified by SymPy\footnote{To see intermediate steps, discussed above, interested
reader can switch on debugging output by setting
\texttt{SYMPY\_DEBUG} environment variable, before importing anything from
the SymPy namespace.}:
